---
title: "Getting Started"
author: "Steven M. Mortimer"
date: "2018-05-18"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

### Authenticate
First, load the `squareupr` package and login. There are two ways to authenticate: 
1) OAuth 2.0 or a 2) Personal Access Token (PAT). It is recommended to use OAuth 2.0 so that 
your PAT does not have to be shared/embedded within scripts. However, note that before 
using OAuth 2.0 authentication it is necessary that you set up your own Connected App 
in the Square dashboard. An App ID and App Secret will be provided, then you will 
be able to plug into your script like so: 

```{r other-params, eval=FALSE}
options(squareupr.app_id = "sq0-99-thisisatest99connected33app22id")
options(squareupr.app_secret = "sq0-Th1s1sMyAppS3cr3t")
sq_auth()
```

OAuth 2.0 User credentials will be stored in locally cached file entitled ".httr-oauth-squareupr" 
in the current working directory.

```{r auth, include = FALSE}
library(dplyr)
library(squareupr)
settings <- readRDS(here::here("tests", "testthat", "squareupr_test_settings.rds"))
suppressMessages(sq_auth(personal_access_token = settings$personal_access_token, 
                         verbose = FALSE))
```

```{r, eval=FALSE}
library(dplyr)
library(squareupr)

# Using Personal Access Token (PAT)
sq_auth(personal_access_token = "sq-Th1s1sMyPers0nalAcessT0ken")

# Using OAuth 2.0 authentication
sq_auth()
```

### Get Transactions
Transactions are organized by location. With the v2 Locations endpoint you can pull 
information regarding all locations first to obtain the location IDs. Then with the 
`sq_list_transactions()` function you can provide the location and timeframe to search. 
The function defaults to pulling transactions from the previous day using `Sys.Date() - 1`. 
Once you obtain the transactions the `tenders` field lists all methods of payment 
used to pay in the transaction.

```{r transactions-by-location}
# list all locations
our_locations <- sq_list_locations()
our_transactions <- sq_list_transactions(location = our_locations$id[2], 
                                         begin_time = as.Date('2018-05-11'), 
                                         end_time = as.Date('2018-05-12'))
our_transactions
```

### Get Customers
Once you pull data about transactions you can take the customer_id from the transaction 
`tenders` field and match that up with customer details. In Square customers can 
be placed into groups that allow for the analysis of transactions at a group-level.

```{r customers}
# list customers created in the last 90 days
created_start <- format(Sys.Date()-90, '%Y-%m-%dT00:00:00-00:00')
created_end <- format(Sys.Date(), '%Y-%m-%dT00:00:00-00:00')
our_customers <- sq_search_customers(query = list(filter=
                                                    list(created_at=
                                                           list(start_at=created_start,
                                                                end_at=created_end))))
our_customers$given_name <- "{HIDDEN}"
our_customers$family_name <- "{HIDDEN}"
our_customers %>% select(id, created_at, updated_at, 
                         given_name, family_name, preferences, groups)

# show the groups that each customer belongs to
# filter to the groups designated automatically by Square
sq_extract_cust_groups(our_customers) %>%
  filter(grepl("^CQ689YH4KCJMY", groups.id))
```

### Check out the Tests
The **squareupr** package has quite a bit of unit test coverage to track any 
changes made between newly released versions of the Square APIs. These tests are 
great source of examples for how to interect with the API. The tests are available 
<a target="_blank" href="https://github.com/StevenMMortimer/squareupr/tree/master/tests/testthat">here</a>.
